DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-07 paper/intro.tex
intro revision

% what are our findings?
From our experiments, we discover that the DeepPicar is capable of 
completing control loops in under 50 ms, or 20 hz, and can do so 
almost 99\% of the time. The number of cores used by the platform has 
an unexpectedly low impact on its performance, only decreasing the 
control loop times by 30\% when using 4 cores instead of 1.  Our 
platform shows the potential to run multiple neural network models 
simultaneously as there are no indications of direct interference 
between them. Instead, we show that memory intensive co-runners can 
be detrimental to the real-time performance of the DeepPicar. 
Finally, while we find that the Raspberry Pi 3 takes longer to 
complete control loops when compared to other embedded computing 
platforms, namely the Intel UP Board and the NVIDIA Tegra TX2, we 
still conclude that the Pi 3 is a viable option for autonomous 
vehicle research.

>>>>

% what are our findings?
Using the DeepPicar platform, we systematically analyzed its real-time
capabilities in the context of deep-learning based real-time
control, especially on real-time deep neural network inferencing.
We also evaluated other, more powerful, embedded computing
platforms to better understand achievable real-time performance of
DeepPicar's deep-learning based control system and the impact of
computing hardware architectures.

We find that the DeepPicar is capable of 
completing control loops in under 50 ms, or 20 hz, and can do so 
almost 99\% of the time.
Other tested embedded platforms, Intel Up and NVIDIA TX2, offer even
better performance, capable of supporting deep-learning based real-time
control up to 100 Hz control frequency on the TX2 when the GPU is used.
However, in all platforms, shared resource contention remains an
important issue as we observe up to 9.6X control loop execution time
increase, mostly due to increase in the nueral network inferencing
operation, when memory performance intensive applications are
co-scheduled on idle CPU cores.

%% that must be considered in applying deep-learning
%% models on shared memory based embedded computing platforms.
%% The number of cores used to process the neural network by the platform has 
%% an unexpectedly low impact on its performance, only decreasing the 
%% control loop times by 30\% when using 4 cores instead of 1.  Our 
%% platform shows the potential to run multiple neural network models 
%% simultaneously as there are no indications of direct interference 
%% between them. Instead, we show that memory intensive co-runners can 
%% be detrimental to the real-time performance of the DeepPicar. 
%% Finally, while we find that the Raspberry Pi 3 takes longer to 
%% complete control loops when compared to other embedded computing 
%% platforms, namely the Intel UP Board and the NVIDIA Tegra TX2, we 
%% still conclude that the Pi 3 is a viable option for autonomous 
%% vehicle research.
